%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {NYUST Measurement Lab.} % Organization
    {Yunlin, Taiwan} % Location
    {Dec. 2012 - July. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researching and implementing UGV obstacle avoidance algorithms in C++ on embedded Linux.}
        \item {Teaching assistant for Engineering Mathematics.}
        \item {Teaching assistant for Linear Algebra.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {MedicusTek Inc.} % Organization
    {Taipei, Taiwan} % Location
    {Dec. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing and implementing an IoT gateway to communicate and monitor multiple IoT devices with Bluetooth.}
        \item {Designing the data model and some data transformation algorithm in Python.}
        \item {Designing and implementing services on Linux backend system which receives data from multiple IoT devices and using ZeroMQ to communicate with other services.}
        \item {Designing and implementing a backup and data storage backend system on Linux.}
        \item {Using Vagrant, Packer and Ansible to automatically create development and production environment.}
        \item {Software Tech. Leader, responsible for designing and coordinating the work-flow between other departments.}
      \end{cvitems}
    }

\end{cventries}
